% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

\exhyphenpenalty=10000
\hyphenpenalty=10000

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=17mm, cutspace=0mm,
                 topspace=8mm, bottomspace=12mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[12pt, arial]

\setupwhitespace[small]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfc, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfa\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\tfa\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=\tfa,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed, itemsep=2mm]   % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[center]},
   indentnext=no,
  ]


\starttext

\section[cory-robinson]{Cory Robinson}

\startblockquote
\useURL[url1][mailto:robinson.cory.r@gmail.com][][robinson.cory.r@gmail.com]\from[url1]
* (903) 331-8025\crlf
\useURL[url2][http://linkedin.com/pub/cory-robinson/15/76a/939/]\from[url2]\crlf
Houston, Texas
\stopblockquote

\thinrule

~\crlf
\strut ~\crlf
\strut ~

Dear Python Developer Team at Integrated Informatics,\crlf
\strut ~\crlf
I am exploring new career opportunities in the Houston area, and you
posing for a Python Software Engineer on LinkedIn certainly caught my
eye! I have included my resume as the second page to this document for
your review. I would just like to take a moment to elaborate on some of
my experience and why I think I am a good fit for this job.\crlf
\strut ~\crlf
I've been working in the oil & gas industry for about a year and a half
now as a Data Processing Geophysicist. While my job is to process
subsurface seismic imaging data, using GIS tools and mapping is also a
normal part of my job function. Now, when I say GIS tools, it is some
basic Google Earth stuff where I look at the coordinate layout of our
projects and check elevations, and sometimes I get to draw out paths and
measure distances in the area that I am analyzing as well as overlay
topographical maps. I also use Python sometimes to interpolate
coordinates and elevations, and also some other kinds of file
manipulations. I started learning Python when I was taking undergraduate
math classes. My programming experience in Python, and other languages
was greatly intensified when I started grad school at the University of
Washington. I have become very familiar with numpy, scipy, and several
other Python libraries. I've written tests, and used the pdb debugger,
and I try to abide by PEP-8 when I write code. I've used git for version
control and Github and Bitbucket for code repos. I know quite a bit
about Python, but I haven't done any development as a full-time
professional. The closest thing to a commercial application that I have
worked on is a personal side project that I started working on this year
-- an algorithmic currency trading system. The project is written in
Python, and so far it streams real-time currency data from a brokerage,
and can make real-time fake trades on my practice account. I'm currently
in the stage of writing a backtesting engine so that I can implement and
test my trading strategies.\crlf
\strut ~\crlf
I'm not a Senior Software Engineer, but I know my way around Python. I
am a quick learner, and I certainly have the interest and motivation to
dive right into a role developing software for GIS applications with
Python! I would definitely like to have a chance for us to talk and
learn more about each other! I can be reached quickly by email to
schedule a time for a phone conference or an in-person interview. Please
see my contact information at the top of my resume. Thank you very much
for your time and consideration, and I hope to hear from you soon!\crlf
\strut ~\crlf
Regards,\crlf
Cory Robinson

\stoptext
